Target Markdown

### 2023-08-07 _targets.Rmd
take sim_fw from upstream

```{r targets raw_sim}
list(
)

@@

```{targets sem-process}
list(
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z + productivity, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + productivity, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + productivity, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + productivity, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
    )
    ),
  tar_target(sem, as.psem(sem_model_list)),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
      #filter(abs(Std.Estimate) > 0.1)# %>%
#  mutate(
#    Response = var_replacement()[Response],
#    Predictor = var_replacement()[Predictor]
#  ) %>%
    }),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

```{targets p-stab-rich}
list(
  tar_target(p_stab_s_prod,
    sim_fw %>%
      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .2) %>%
      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.2, .6), rho == 0, productivity == 5) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .2) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

@@

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

@@

```{targets p-omn}
list(
  tar_target(p_omn_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .2) %>%
      pivot_longer(c(stab_com, pop_stab, async
          ), names_to = "stab_comp", values_to = "values") %>%
      mutate(stab_comp = var_replacement()[stab_comp]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg omnivory", y = "Stability component") +
      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
      theme_bw()),
  tar_target(p_omn_fw,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .2) %>%
      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
          ), names_to = "fw_str", values_to = "values") %>%
      mutate(fw_str = var_replacement()[fw_str]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg. Omnivory", y = "Food-web structure") +
      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
      theme_bw()
  )
)
```

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .2) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_cor, tar_simple = TRUE}
cor_var <- cor(
  sim_fw %>%
    select(c(richness, ct_alive, Z, bm_total,
        avg_int_strength, avg_omnivory, max_tlvl,
        rho, env_stoch, productivity,
        stab_com, pop_stab, async, sae_total, sae_even,
        evenness_sae, cpe, cpe_int, cpe_env)) %>%
  na.omit() %>%
  rename(any_of(get_rev_vec_name_val(var_replacement()))),
    method = "spearman")
ggcorrplot(cor_var, type = "lower", lab = TRUE)
```

@@

```{r, message = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(ggcorrplot)
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```

```{r}
tar_load(sim_prep)
map(sim_prep$omega[1:5], length)
```

```{r}
tar_load(sim_fw)
colnames(sim_fw)
summary(sim_fw$avg_int_strength)
unique(sim_fw$Z)
tar_read(p_cor)
tar_read(p_prod_pop_stab)
tar_read(p_stab_s_stress)

sim_fw %>%
  filter(env_stoch == .2, rho %in% c(0, .4, 1), productivity == 5) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .2, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

@@

@@

sim_sp %>%
  filter(env_stoch == .2, rho == 1, Z == 10) %>%
  ggplot(aes(x = tlvl, y = log(cv_sp))) +
  geom_point() +
  geom_smooth()
```

```{r}

tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .1)
tar_read(sem_rsquared)
tar_load(sem_collinearity)
sem_collinearity %>%
  print(., n = 38)
```

@@

  )
summary(mod_tot)
predict(mod_tot)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

@@

```{r}
pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho))

>>>>

```{r targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, readRDS(sim_fw_file)),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

>>>>>>> Stashed changes

@@

```{targets sem-process}
list(
  tar_target(sem_model_list,
    list(
      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      #richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + h, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + h, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
    )
    ),
  tar_target(sem, as.psem(sem_model_list)),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
      #filter(abs(Std.Estimate) > 0.1)# %>%
#  mutate(
#    Response = var_replacement()[Response],
#    Predictor = var_replacement()[Predictor]
#  ) %>%
    }),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0, productivity == 5) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

@@

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

@@

```{targets p-omn}
list(
  tar_target(p_omn_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(stab_com, pop_stab, async
          ), names_to = "stab_comp", values_to = "values") %>%
      mutate(stab_comp = var_replacement()[stab_comp]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg omnivory", y = "Stability component") +
      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
      theme_bw()),
  tar_target(p_omn_fw,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
          ), names_to = "fw_str", values_to = "values") %>%
      mutate(fw_str = var_replacement()[fw_str]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg. Omnivory", y = "Food-web structure") +
      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
      theme_bw()
  )
)
```

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_cor, tar_simple = TRUE}
cor_var <- cor(
  sim_fw %>%
    select(c(richness, ct_alive, Z, bm_total,
        avg_int_strength, avg_omnivory, max_tlvl,
        w_avg_tlvl,
        rho, env_stoch, h,
        stab_com, pop_stab, async, sae_total, sae_even,
        evenness_sae, cpe, cpe_int, cpe_env)) %>%
  na.omit() %>%
  rename(any_of(get_rev_vec_name_val(var_replacement()))),
    method = "spearman")
ggcorrplot(cor_var, type = "lower", lab = TRUE)
```

@@

```{r, message = FALSE}
library(targets)
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)
library(piecewiseSEM)
library(semEff)
library(easystats)
library(glmmTMB)
library(ggcorrplot)
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```

```{r}
tar_load(c(sim_fw))
colnames(sim_fw)
summary(sim_fw$avg_int_strength)
unique(sim_fw$env_stoch)
tar_read(p_cor)
tar_read(p_prod_pop_stab)
tar_read(p_stab_s_stress)
tar_read(p_ct_stab)
tar_read(p_rich_stab)

summary(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
summary(lm(cpe_int ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
summary(lm(cpe ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
performance::check_collinearity(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
mod_cpe <- lm(cpe ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
summary(mod_cpe_int)
performance::check_collinearity(mod_cpe_int)

mod_cpe <- lm(log(cpe) ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)

summary(mod_cpe)
plot(mod_cpe)
performance::check_collinearity(mod_cpe_int)

sim_fw %>%
  filter(env_stoch == 0.3, rho %in% c(0, .5, 1), productivity == 5) %>%
  ggplot(aes(x = richness, y = cpe_env, color = as.factor(rho))) +
  geom_point() +
  labs(x = "Species richness", y = "Comp. effects (Environment)") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .6, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = pop_stab, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

sim_fw %>%
  filter(env_stoch == .3, rho == 0) %>%
  ggplot(aes(x = as.factor(productivity), y = stab_com, color = as.factor(Z))) +
  geom_boxplot() +
  labs(x = "Productivity", y = "Population stability") +
  theme_bw()

@@

```{r}
unique(sim_fw$Z)
```

```{r}
sim_fw %>%
  filter(
    rho %in% c(0), productivity == 5, env_stoch == .5
    ) %>%
  ggplot(aes(y = stab_pop, x = as.factor(Z))) +
  geom_boxplot()
```

```{r}
sim_fw %>%
  filter(
    rho %in% c(0), productivity == 5, env_stoch == .5,
    Z == 500
    ) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, stab_pop
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = as.factor(richness), y = values)) +
  geom_boxplot() +
  labs(x = "Connectance", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{r}
tar_load(sim_fw_cons)
sim_fw_cons %>%
  filter(env_stoch == .6, rho == 1, Z == 100, productivity == 5) %>%
  ggplot(aes(x = richness, y = stab_com, color = as.factor(h))) +
  geom_point() +
  geom_smooth()

sim_fw %>%
  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 15) %>%
  ggplot(aes(x = richness, y = async, color = as.factor(h))) +
  geom_point() +
  geom_smooth()

sim_fw_cons %>%
  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 30) %>%
  ggplot(aes(x = richness, y = pop_stab, color = as.factor(h))) +
  geom_point() +
  geom_smooth()
```

```{r}
plot(richness ~ Z, sim_fw)
```

@@

sim_sp %>%
  filter(env_stoch == .3, rho == 1, Z == 100) %>%
  ggplot(aes(x = tlvl, y = log(cv_sp))) +
  geom_point() +
  geom_smooth()
```

```{r}
tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .05)
tar_read(sem_rsquared)
tar_load(sem_collinearity)
sem_collinearity %>%
  print(., n = 38)
```

@@

  )
summary(mod_tot)
predict(mod_tot)
summary(sim_fw$stab_com)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

@@

```{r}
p_pred_sr_ct_int <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_ct_int.png"),
  plot = p_pred_sr_ct_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
p_pred_sr_omn <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1),
    rho %in% c(0, 1),
    avg_int_strength %in% .02,
    avg_omnivory %in% c(.01, .1),
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(avg_omnivory))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_omn.png"),
  plot = p_pred_sr_omn,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

p_pred_sr_avg_tlvl <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1),
    rho %in% c(0, 1),
    avg_int_strength %in% .02,
    avg_omnivory %in% c(.05),
    w_avg_tlvl == c(1.5, 2)) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(w_avg_tlvl))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_avg_tlvl.png"),
  plot = p_pred_sr_avg_tlvl,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
